### 2020-07-30 README.Rmd
- Add `ResamplingSptCVCluto` (#53)

| Literature                | Package     | Reference     | mlr3 Sugar                     |
| ---------------           | ---------   | ---------     | ---------------                |
| Spatial Buffering         | blockCV     | Valavi 2019   | `rsmp("spcv-buffer")`          |
| Spatial Blocking          | blockCV     | Valavi 2019   | `rsmp("spcv-block")`           |
| Spatial CV                | sperrorest  | Brenning 2012 | `rsmp("spcv-coords")`          |
| Environmental Blocking    | blockCV     | Valavi 2019   | `rsmp("spcv-env")`             |
| ---                       | ---         | ---           | ---                            |
| Repeated Spatial Blocking | blockCV     | Valavi 2019   | `rsmp("repeated-spcv-block")`  |
| Repeated Spatial CV       | sperrorest  | Brenning 2012 | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking     | blockCV     | Valavi 2019   | `rsmp("repeated-spcv-env")`    |

@@

| Name     | Code              | Type    |
| ---      | ---               | ---     |
| ecuador  | `tsk("ecuador")`  | Classif |
| diplodia | `tsk("diplodia")` | Classif |
| cookfarm | `tsk("cookfarm")` | Regr    |

@@

task <- tsk("ecuador")
resampling <- rsmp("spcv-coords", folds = 5)
resampling$instantiate(task)

@@

>>>>

| Literature                | Package     | Reference     | mlr3 Sugar                     |
| ---------------           | ---------   | ---------     | ---------------                |
| Spatial Buffering         | blockCV     | Valavi 2019   | `rsmp("spcv-buffer")`          |
| Spatial Blocking          | blockCV     | Valavi 2019   | `rsmp("spcv-block")`           |
| Spatial CV                | sperrorest  | Brenning 2012 | `rsmp("spcv-coords")`          |
| Environmental Blocking    | blockCV     | Valavi 2019   | `rsmp("spcv-env")`             |
|           -               | -           | -             | `rsmp("spcv-cluto")`           |
| ---                       | ---         | ---           | ---                            |
| Repeated Spatial Blocking | blockCV     | Valavi 2019   | `rsmp("repeated-spcv-block")`  |
| Repeated Spatial CV       | sperrorest  | Brenning 2012 | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking     | blockCV     | Valavi 2019   | `rsmp("repeated-spcv-env")`    |
|           -               | -           | -             | `rsmp("repeated-spcv-cluto")`  |

@@

| Name     | Code              | Type    |
| ---      | ---               | ---     |
| ecuador  | `tsk("ecuador")`  | Classif |
| diplodia | `tsk("diplodia")` | Classif |

## Spatiotemporal tasks

| Name     | Code              | Type    |
| ---      | ---               | ---     |
| cookfarm | `tsk("cookfarm")` | Regr    |

@@

task = tsk("ecuador")
resampling = rsmp("spcv-coords", folds = 5)
resampling$instantiate(task)

@@

### Spatiotemporal Visualization

Three-dimensional visualization via {plotly}

```{r spatiotemp, eval=FALSE}
library(plotly)
task_st = tsk("cookfarm")
resampling = rsmp("spcv-cluto", folds = 5)
resampling$instantiate(task_st, time_var = "Date")
autoplot(resampling, task_st, fold_id = 1, point_size = 3)
```

![](man/figures/spt-viz.png)
